### 2022-01-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@d40d6d0710dd8c097b5a8838037bd0b10591c046 🚀

Graph embedding is a varied family of machine learning techniques aiming
to transform nodes and edges into a vector space, usually of a lower
dimension, whilst maximally retaining key properties of the graph.
Ecological networks are an interesting candidate for the widespread
application of embeddings, as they tend to posess a shared sstructural
backbone (Mora et al., 2018), which hints at structural invariants that
can be revealed a lower dimensions. Indeed, previous work by Eklöf et
al. (2013) suggests that food webs are inherently low-dimensional
objects, and can be adequately represented with less than ten
dimensions.

@@

\begin{longtable}[]{@{}lll@{}}
\toprule
Method & Embedded object & Reference\tabularnewline
\midrule
\endhead
DeepWalk & graph walk & Perozzi et al. (2014)\tabularnewline
node2vec & node embedding & Grover \& Leskovec (2016)\tabularnewline
graph2vec & sub-graph embedding & Narayanan et al. (2017)\tabularnewline
SDNE & nodes through auto-encoding & Wang et al. (2016)\tabularnewline
\bottomrule
\end{longtable}

@@

@@

@@

@@

>>>>

Graph embedding is a varied family of machine learning techniques aiming
to transform nodes and edges into a vector space, usually of a lower
dimension, whilst maximally retaining key properties of the graph (Yan
et al., 2005). Ecological networks are an interesting candidate for the
widespread application of embeddings, as they tend to posess a shared
sstructural backbone (Mora et al., 2018), which hints at structural
invariants that can be revealed a lower dimensions. Indeed, previous
work by Eklöf et al. (2013) suggests that food webs are inherently
low-dimensional objects, and can be adequately represented with less
than ten dimensions.

@@

\begin{longtable}[]{@{}lll@{}}
\toprule
Method & Embedding approach & Reference\tabularnewline
\midrule
\endhead
DeepWalk & graph walk & Perozzi et al. (2014)\tabularnewline
FastEmbed & graph through PCA/SVD analogue & Ramasamy \& Madhow
(2015)\tabularnewline
LINE & nodes through statistical divergence & Tang et al.
(2015)\tabularnewline
SDNE & nodes through auto-encoding & Wang et al. (2016)\tabularnewline
node2vec & node embedding & Grover \& Leskovec (2016)\tabularnewline
graph2vec & sub-graph embedding & Narayanan et al. (2017)\tabularnewline
HARP & nodes through a meta-strategy & Chen et al. (2017)\tabularnewline
\bottomrule
\end{longtable}

@@

\leavevmode\hypertarget{ref-Chen2017HarHie}{}%
Chen, H., Perozzi, B., Hu, Y., \& Skiena, S. (2017, November 16).
\emph{HARP: Hierarchical Representation Learning for Networks}.
\url{http://arxiv.org/abs/1706.07845}

@@

\leavevmode\hypertarget{ref-Ramasamy2015ComSpe}{}%
Ramasamy, D., \& Madhow, U. (2015). Compressive spectral embedding:
Sidestepping the SVD. In C. Cortes, N. Lawrence, D. Lee, M. Sugiyama, \&
R. Garnett (Eds.), \emph{Advances in neural information processing
systems} (Vol. 28). Curran Associates, Inc.
\url{https://proceedings.neurips.cc/paper/2015/file/4f6ffe13a5d75b2d6a3923922b3922e5-Paper.pdf}

@@

\leavevmode\hypertarget{ref-Tang2015LinLar}{}%
Tang, J., Qu, M., Wang, M., Zhang, M., Yan, J., \& Mei, Q. (2015). LINE:
Large-scale Information Network Embedding. \emph{Proceedings of the 24th
International Conference on World Wide Web}, 1067--1077.
\url{https://doi.org/10.1145/2736277.2741093}

@@

\leavevmode\hypertarget{ref-Yan2005GraEmb}{}%
Yan, S., Xu, D., Zhang, B., \& Zhang, H.-J. (2005). Graph embedding: A
general framework for dimensionality reduction. \emph{2005 IEEE Computer
Society Conference on Computer Vision and Pattern Recognition
(CVPR'05)}, \emph{2}, 830--837 vol. 2.
\url{https://doi.org/10.1109/CVPR.2005.170}
